Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-20 paper/structureScene.tex
Add DCASE2016 class-wise results

\begin{table}
\begin{center}
\caption{Class-wise accuracies on the development part of the DCASE 2016 dataset.\label{table:dcase2016}}
\begin{tabular}{lcc}
Features & MFCCs & log-scattering \\
\midrule
beach & $58.3 \pm 28.2$ & $83.5 \pm \phantom{0}7.1$ \\
bus & $58.2 \pm 25.4$ & $88.8 \pm 11.4$ \\
cafe/restaurant & $77.4 \pm 14.7$ & $64.5 \pm \phantom{0}8.3$ \\
car & $92.3 \pm \phantom{0}7.7$ & $94.9 \pm \phantom{0}6.1$ \\
city\_center & $96.4 \pm \phantom{0}3.8$ & $91.7 \pm \phantom{0}9.4$ \\
forest\_path & $67.7 \pm 30.8$ & $93.8 \pm \phantom{0}7.8$ \\
grocery\_store & $44.7 \pm 24.8$ & $90.9 \pm \phantom{0}6.9$ \\
home & $44.8 \pm 15.3$ & $56.2 \pm 23.9$ \\
library & $54.6 \pm 20.3$ & $82.0 \pm 13.0$ \\
metro\_station & $94.7 \pm \phantom{0}6.8$ & $96.0 \pm \phantom{0}2.3$ \\
office & $95.7 \pm \phantom{0}7.5$ & $87.5 \pm 21.7$ \\
park & $52.4 \pm 10.4$ & $75.4 \pm \phantom{0}7.4$ \\
residential\_area & $53.2 \pm 17.0$ & $44.2 \pm 15.0$ \\
train & $44.5 \pm 23.1$ & $58.3 \pm 10.0$ \\
tram & $52.1 \pm 11.9$ & $83.7 \pm 12.2$ \\
\bottomrule
Average & $65.8 \pm \phantom{0}8.0$ & $79.4 \pm \phantom{0}3.0$ \\
\end{tabular}
\end{center}

@@

In order to evaluate the generality of our findings, we have taken part in the acoustic scene classification task of the 2016 edition of the DCASE challenge, which was evaluated on a much larger dataset compared to DCASE 2013. For this reason, training support vector machines with the Gaussian RBF kernel proved computationally too demanding and we instead used a linear kernel. Results on DCASE 2013 (see Table \ref{table:dcase2013}) suggests that this provides comparable, albeit slightly worse results.

We compare our results with baseline classifier using linear SVMs and MFCC features, which achieves an average accuracy of $65.5\%$. With the scattering transform, however, the average accuracy increases to $79.4\%$. This accuracy increases slightly to $80.8\%$ when calculated on the held-out evaluation dataset.\footnote{\url{http://www.cs.tut.fi/sgn/arg/dcase2016/task-results-acoustic-scene-classification}} The small change in accuracy suggests that there is little overfitting in the model, an indication of good generalization power.

>>>>

\begin{table}
\begin{center}
\caption{Class-wise accuracies on the DCASE 2016 dataset.\label{table:dcase2016}}
\begin{tabular}{lccc}
Features & MFCCs & log-scattering & log-scattering \\
Subset & development & development & evaluation \\
\midrule
beach & $58.3 \pm 28.2$ & $83.5 \pm \phantom{0}7.1$ & $80.8$\\
bus & $58.2 \pm 25.4$ & $88.8 \pm 11.4$ & $92.3$ \\
cafe/restaurant & $77.4 \pm 14.7$ & $64.5 \pm \phantom{0}8.3$ & $50.0$ \\
car & $92.3 \pm \phantom{0}7.7$ & $94.9 \pm \phantom{0}6.1$ & $96.2$ \\
city\_center & $96.4 \pm \phantom{0}3.8$ & $91.7 \pm \phantom{0}9.4$ & $84.6$ \\
forest\_path & $67.7 \pm 30.8$ & $93.8 \pm \phantom{0}7.8$ & $96.2$ \\
grocery\_store & $44.7 \pm 24.8$ & $90.9 \pm \phantom{0}6.9$ & $84.6$ \\
home & $44.8 \pm 15.3$ & $56.2 \pm 23.9$ & $80.8$ \\
library & $54.6 \pm 20.3$ & $82.0 \pm 13.0$ & $65.4$ \\
metro\_station & $94.7 \pm \phantom{0}6.8$ & $96.0 \pm \phantom{0}2.3$ & $96.2$ \\
office & $95.7 \pm \phantom{0}7.5$ & $87.5 \pm 21.7$ & $100$ \\
park & $52.4 \pm 10.4$ & $75.4 \pm \phantom{0}7.4$ & $65.4$ \\
residential\_area & $53.2 \pm 17.0$ & $44.2 \pm 15.0$ & $69.2$ \\
train & $44.5 \pm 23.1$ & $58.3 \pm 10.0$ & $53.8$ \\
tram & $52.1 \pm 11.9$ & $83.7 \pm 12.2$ & $96.2$ \\
\bottomrule
Average & $65.8 \pm \phantom{0}8.0$ & $79.4 \pm \phantom{0}3.0$ & $80.8$ \\
\end{tabular}
\end{center}

@@

In order to evaluate the generality of our findings, we have taken part in the acoustic scene classification task of the 2016 edition of the DCASE challenge, which was evaluated on a much larger dataset compared to DCASE 2013. For this reason, training support vector machines with the Gaussian RBF kernel proved computationally too demanding and we instead used a linear kernel. Results on DCASE 2013 (see Table \ref{table:dcase2013}) suggests that this provides comparable, albeit slightly worse results. The results on DCASE 2016 (see Table \ref{table:dcase2016}).

We compare our results with baseline classifier using linear SVMs and MFCC features, which achieves an average accuracy of $65.5\%$. With the scattering transform, however, the average accuracy increases to $79.4\%$. This accuracy increases slightly to $80.8\%$ when calculated on the held-out evaluation dataset.\footnote{\url{http://www.cs.tut.fi/sgn/arg/dcase2016/task-results-acoustic-scene-classification}} The small change in overall accuracy and relatively stable class-wise accuracies suggest that there is little overfitting in the model, an indication of good generalization power.
